R Notebook

### 2023-02-24 FEM_R/Loneliness_Social_Isolation/rough_working_script.Rmd
Updated the settings.csv and .txt files with the new vars for the loneliness and social isolation scenario runs. Also wrote a utilities function in R for collating detailed output files, and some more variable checking in the R working scripts. Also imputed some things in kludge.do, and need to investigate why lnly values are not being imputed properly

```{r}
## Directories
base_output_dir <- "output/COMPLETE/"
input_dir <- "input_data/"
## Inputs
long <- read_dta(paste0(input_dir, 'ELSA_long.dta'))
stock <- read_dta(paste0(input_dir, 'ELSA_stock.dta'))
repl <- read_dta(paste0(input_dir, 'ELSA_repl.dta'))
trans <- read_dta(paste0(input_dir, 'ELSA_transition.dta'))
## Outputs
### Baseline
base <- read_dta(paste0(base_output_dir, 'ELSA_core_base/ELSA_core_base_summary.dta'))
cohort <- read_dta(paste0(base_output_dir, 'ELSA_core_cohort/ELSA_core_cohort_summary.dta'))
### Cross-Validation
cv1 <- read_dta(paste0(base_output_dir, 'ELSA_CV1/ELSA_CV1_summary.dta'))
#cv1.full <- read_dta(paste0(base_output_dir, 'ELSA_CV1/detailed_output/ELSA_CV1_summary.dta'))
cv2 <- read_dta(paste0(base_output_dir, 'ELSA_CV2/ELSA_CV2_summary.dta'))
### Interventions
#no.lonely <- read_dta(paste0(base_output_dir, 'ELSA_nolnly_cohort/ELSA_nolnly_cohort_summary.dta'))
#no.sociso <- read_dta(paste0(base_output_dir, 'ELSA_nosociso_cohort/ELSA_nosociso_cohort_summary.dta'))
#no.lnly.sociso <- read_dta(paste0(base_output_dir, 'ELSA_nolnly_nosociso_cohort/ELSA_nolnly_nosociso_cohort_summary.dta'))
```

>>>>

```{r}
## Directories
base_output_dir <- "output/LNLY_SOCISO_TEST/"
input_dir <- "input_data/"
## Inputs
long <- read_dta(paste0(input_dir, 'ELSA_long.dta'))
stock <- read_dta(paste0(input_dir, 'ELSA_stock.dta'))
repl <- read_dta(paste0(input_dir, 'ELSA_repl.dta'))
trans <- read_dta(paste0(input_dir, 'ELSA_transition.dta'))
## Outputs
### Baseline
base <- read_dta(paste0(base_output_dir, 'ELSA_core_base/ELSA_core_base_summary.dta'))
base.detail <- read_dta(paste0(base_output_dir, 'ELSA_core_base/ELSA_core_base_summary.dta'))
cohort <- read_dta(paste0(base_output_dir, 'ELSA_core_cohort/ELSA_core_cohort_summary.dta'))
### Cross-Validation
#cv1 <- read_dta(paste0(base_output_dir, 'ELSA_CV1/ELSA_CV1_summary.dta'))
#cv1.full <- read_dta(paste0(base_output_dir, 'ELSA_CV1/detailed_output/ELSA_CV1_summary.dta'))
#cv2 <- read_dta(paste0(base_output_dir, 'ELSA_CV2/ELSA_CV2_summary.dta'))
### Interventions
#no.lonely <- read_dta(paste0(base_output_dir, 'ELSA_nolnly_cohort/ELSA_nolnly_cohort_summary.dta'))
#no.sociso <- read_dta(paste0(base_output_dir, 'ELSA_nosociso_cohort/ELSA_nosociso_cohort_summary.dta'))
#no.lnly.sociso <- read_dta(paste0(base_output_dir, 'ELSA_nolnly_nosociso_cohort/ELSA_nolnly_nosociso_cohort_summary.dta'))
```

```{r}
detailed_output_append <- function(base.out.dir, scenario) {
  ## function to read in all files in a detailed output and collect into 1 object

  path <- paste0('output/', base.out.dir, scenario, 'detailed_output/')

  filelist <- list.files(path,
                         full.names = TRUE)
  return(do.call(rbind, lapply(filelist, read_dta)))
}

path <- 'output/LNLY_SOCISO_TEST/ELSA_core_base/detailed_output/'

base.detail <- detailed_output_append(base.out.dir = base_output_dir, scenario = 'ELSA_core_base')
